Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-05-26 source/sec_exp_note.tex
add linear regression
exp section version 1

\section{Numerical Experiments}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{fig/synthetic_linear_regression_1k_6k-epsilon001-logTrue-epoch-1-2-3-4-b4-adapt0.pdf} & 
\includegraphics[width=0.5\textwidth]{fig/iteration_EandN-synthetic_linear_regression_1k_6k-epsilon01.pdf} 
 \\
(a) $\epsilon=0.01$  & (b) $N/E = 10$ 
\end{tabular}
	\caption{The linear speed up w.r.t the number of nodes. The synthetic dataset has $6000$ samples, evenly distributed on $10, 20, 30, 40, 50, 60, 80, 100, 200, 300, 400, 500, 600, 750, 1000$ devices. The figure shows the number of iterations needed to converge to $\epsilon$. The learning rate is decayed as the $\eta_t = \frac{1}{c + t \times a}$, where we extensively search the best learning rate $c \in \{1, 10\}$ and $a \in \{1\mathrm{e}{-2}, 1\mathrm{e}{-3}, 1\mathrm{e}{-4}, 1\mathrm{e}{-5}, 1\mathrm{e}{-6}\}$ for each configuration. Batch size is 4 in this case.}
\end{figure}

>>>>

\section{Numerical Experiments}
\subsection{Strongly Convex}

\begin{figure}[h!]
\centering
\begin{tabular}{cc}
	\includegraphics[width=0.45\textwidth]{fig/paper-stronglycvxsmthspeedupNodesT-min-w8a-epsilon0131-reg1e-05.pdf} & 
\includegraphics[width=0.45\textwidth]{fig/paper-stronglycvxsmthspeedupEpochsT-min-w8a-epsilon0131-reg1e-05.pdf} \\
\end{tabular}
	\caption{Logistic regression with regularization $1e-5$. The linear speed up w.r.t the number of nodes and number of epochs. The synthetic dataset has $N=49749$ samples, evenly distributed on $1, 2, 4, 8, 16, 32$ devices. The figure shows the number of iterations/rounds needed to converge to $\epsilon-$accuracy, where $\epsilon=0.005$. The learning rate is decayed as the $\eta_t = \min(32, \frac{Nc}{1 + t})$, where we extensively search the best learning rate $c \in \{2^{-1}c, 2^{-2}c, c, 2c, 2^{2}c\}$ and for each configuration. Batch size is 4 in this case.}
\end{figure}

\subsection{Convex smooth objective}

\begin{figure}[h!]
\centering
\begin{tabular}{cc}
	\includegraphics[width=0.45\textwidth]{fig/paper-cvxsmoothspeedupNodesT-min-w8a-epsilon0134-reg0.pdf} & 
\includegraphics[width=0.45\textwidth]{fig/paper-cvxsmoothspeedupEpochsT-min-w8a-epsilon0134-reg0.pdf} \\
\end{tabular}
	\caption{Logistic regression without regularization. The linear speed up w.r.t the number of nodes and number of epochs. The w8a dataset has $N=49749$ samples, evenly distributed on $1, 2, 4, 8, 16, 32, 64, 128, 256, 512, 1024$ devices. The figure shows the number of iterations needed to converge to $\epsilon-$accuracy, where $\epsilon=0.02$. The learning rate is decayed as the $\eta_t = \min(\eta_0, \frac{Nc}{1 + t})$, where we extensively search the best learning rate $c \in \{2^{-1}c, 2^{-2}c, c, 2c, 2^{2}c\}$, $\eta_0 \in \{1, 32\}$ and for each configuration. Batch size is 4 in this case.}
\end{figure}

\subsection{Linear regression}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.5\textwidth]{fig/synthetic_linear_regression_1k_6k-epsilon001-logTrue-epoch-1-2-3-4-b4-adapt0.pdf} & 
\includegraphics[width=0.5\textwidth]{fig/iteration_EandN-synthetic_linear_regression_1k_6k-epsilon01.pdf} 
 \\
(a) $\epsilon=0.01$  & (b) $N/E = 10$ 
\end{tabular}
	\caption{linear regression. The linear speed up w.r.t the number of nodes. The synthetic dataset has $6000$ samples, evenly distributed on $10, 20, 30, 40, 50, 60, 80, 100, 200, 300, 400, 500, 600, 750, 1000$ devices. The figure shows the number of iterations needed to converge to $\epsilon$. The learning rate is decayed as the $\eta_t = \frac{1}{c + t \times a}$, where we extensively search the best learning rate $c \in \{1, 10\}$ and $a \in \{1\mathrm{e}{-2}, 1\mathrm{e}{-3}, 1\mathrm{e}{-4}, 1\mathrm{e}{-5}, 1\mathrm{e}{-6}\}$ for each configuration. Batch size is 4 in this case.}
\end{figure}
